A Data-Driven Framework for Neural Field Modeling

### 2011-01-18 ltx/first_order_framework/LaTeX_Manuscript.tex
edit the app A

% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig1.pdf} 
% \end{center}
% \caption{}
% \label{fig:Figure1}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig2.pdf} 
% \end{center}
% \caption{}
% \label{fig:Figure2}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig3.pdf}
% \end{center}
% \caption{} 
% \label{fig:Figure3}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig4.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure4}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht] 
% \begin{center}
% \includegraphics{fig5.pdf}	
% \end{center}
% \caption{}
% \label{fig:Figure5}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig6.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure6}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig7.pdf}
% \end{center}
% \caption{} 
% \label{fig:Figure7}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig8.pdf} 
% \end{center}
% \caption{} 
% \label{fig:Figure8}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig9.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure9}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig10.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure10}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig11.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure11}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig12.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure12}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig13.pdf}
% \end{center}
% \caption{}
% \label{fig:SensorAndSource}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig14.pdf}
% \end{center}
% \caption{}
% \label{fig:Ch3}
% \end{figure*}
\clearpage
\newpage
\appendix
\section{Time Discretization of the Neural Field Model}
\label{App:Time Discretization} This appendix provides a description of the discretization of the neural field model to form the integro-difference equation (IDE) and provides a proof for the stability of the discrete-time equations. To perform the discretization, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} can be approximated by 
\begin{align}
	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} &=-\zeta v\left( \mathbf{r},t \right) \nonumber \\ 
&+ \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
\end{align}
For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation}, we get 
\begin{equation}
	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}. 
\end{equation}
Now making simplifications, the discrete time form of the model is 
\begin{equation}
	\label{Discrete Time Model1}v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}, 
\end{equation}
where $\xi = 1 - T_s \zeta$.

>>>>

% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig1.pdf} 
% \end{center}
% \caption{}
% \label{fig:Figure1}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig2.pdf} 
% \end{center}
% \caption{}
% \label{fig:Figure2}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig3.pdf}
% \end{center}
% \caption{} 
% \label{fig:Figure3}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig4.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure4}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht] 
% \begin{center}
% \includegraphics{fig5.pdf}	
% \end{center}
% \caption{}
% \label{fig:Figure5}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig6.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure6}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig7.pdf}
% \end{center}
% \caption{} 
% \label{fig:Figure7}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig8.pdf} 
% \end{center}
% \caption{} 
% \label{fig:Figure8}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig9.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure9}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig10.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure10}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig11.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure11}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig12.pdf}
% \end{center}
% \caption{}
% \label{fig:Figure12}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig13.pdf}
% \end{center}
% \caption{}
% \label{fig:SensorAndSource}
% \end{figure*}
% \clearpage
% \newpage
% \begin{figure*}[!ht]
% \begin{center}
% \includegraphics{fig14.pdf}
% \end{center}
% \caption{}
% \label{fig:Ch3}
% \end{figure*}
\clearpage
\newpage
\appendix
\section{Time Discretization of the Neural Field Model}
\label{App:Time Discretization} This appendix provides a description of the discretization of the neural field model to form the integro-difference equation (IDE). To perform the discretization, we used a one-step Euler method, where equation~\ref{FinalFormContinuous} can be approximated by 
\begin{align}
	\label{Euler Approximation}\frac{v\left( \mathbf{r},t+T_s \right) - v\left( \mathbf{r},t\right)}{T_s} &=-\zeta v\left( \mathbf{r},t \right) \nonumber \\ 
&+ \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v\left( \mathbf{r}',t \right)} \right)d\mathbf{r}'}. 
\end{align}
For clarity, we shall index time points in the discrete time form of the model using the subscript $t$ and the next time point as $t+1$. Rearranging equation~\ref{Euler Approximation}, we get 
\begin{equation}
	\label{Euler Approximation2} v_{t+1}\left( \mathbf{r}\right) = v_t\left( \mathbf{r}\right) -T_s \zeta v_t\left( \mathbf{r}\right) + T_s \int_\Omega {w\left( \mathbf{r}-\mathbf{r}' \right)f\left( {v_t\left( \mathbf{r}'\right)} \right)d\mathbf{r}'}. 
\end{equation}
Now making simplifications, the discrete time form of the model is 
\begin{equation}
	\label{Discrete Time Model1}v_{t+1}\left(\mathbf{r}\right) = \xi v_t\left(\mathbf{r}\right) + T_s \int_\Omega { w\left(\mathbf{r}-\mathbf{r}'\right) f\left(v_t\left(\mathbf{r}'\right)\right) d\mathbf{r}'}, 
\end{equation}
where $\xi = 1 - T_s \zeta$.
